---
title: "Agenda"
output: 
  bookdown::html_document2:
    toc: false
    includes:
      after_body: assets/foot.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

<style>
  .title{
    display: none;
  }
</style>

<br>

<div class = "blue">
Hello to all registrants of the 2021 CABW and Cal-SFS Meeting!
 
The **Final Agenda** and the **Presentation and Speaker Index** are both available below. 
 
This past week, you should have all received email reminders from *“SWRCB <no-reply@zoom.us>”* with your Zoom Webinar access link. The [Bioassessment Program CABW Webpage](https://www.waterboards.ca.gov/water_issues/programs/swamp/bioassessment/training.html#cabw) also contains the link to [Register for the Zoom Webinar](https://waterboards.zoom.us/webinar/register/WN_5ln2IwFfTNOi0-vYScP0wQ) for those still interested in registering. By registering, you will be able to participate in Q&A during speaker presentations. If you are not registered, you can access the webinar via the live stream on the [California Water Quality Monitoring Council YouTube page](https://www.youtube.com/channel/UCfq3UT8xzT9In0RUWSMOrxQ). You cannot participate in Q&A if you are watching via the live stream. This meeting will be recorded and posted on the Bioassessment Program CABW Webpage for future viewing.
 
Zoom Webinar protocols for attendees: 

- Chat is disabled

- Showing your video is disabled

- Questions can be submitted via the Zoom Webinar Q&A chat feature

- For assistance on how to use Zoom Webinar and the Q&A chat feature, check out the [Zoom - Help Center](https://support.zoom.us/hc/en-us/articles/115004954946-Joining-and-participating-in-a-webinar-attendee-#h_5e983a7a-c202-4a56-bcc9-b4fb033402ac) for Joining and Participating in a Webinar.

- General questions/concerns please contact [SWAMP](swamp@waterboards.ca.gov).

 
Thank you all for registering and supporting this event! Your attendance and participation, especially in these recent years, has been overwhelmingly appreciated.

</div>

<br>

<div class = "row">
  
## **Agenda**

```{r, out.height='600px', out.width='100%', dpi=300, out.extra='style="background-color: #9ecff7; padding:6px; display: inline-block;"'}
include_graphics("images/2021-california-aquatic-bioassessment-workgroup-meeting-agenda.pdf")
```

<br>

## **Presentation and Speaker Index**

```{r, out.height='600px', out.width='100%', dpi=300, out.extra='style="background-color: #9ecff7; padding:6px; display: inline-block;"'}
include_graphics("images/2021_cabw_presentation-and-speaker-index.pdf")
```



</div>

<br>

