---
title: "Session A"
output: 
  bookdown::html_document2:
    includes:
      after_body: assets/foot.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)

```

<br>
<br>

<div class = "row">
  
## [Turning Up The Heat](posters/DePalma-Dow_Angela_TurningUpTheHeatPoster_July2020.pdf)

<br>

 - **Author**, *Affiliation*
 
 [optional photo of author](jpg here)
 
 > Brief bio of author or one sentence summary of poster results, objective, or message.

```{r posterA, out.height='600px', out.width='100%', dpi=300, out.extra='style="background-color: #9ecff7; padding:6px; display: inline-block;"'}

include_graphics("posters/DePalma-Dow_Angela_TurningUpTheHeatPoster_July2020.pdf")

```

</div>

<br><br>

<div class = "row">

## [Using sensitive montane species as indicators of hydroclimatic change in meadow ecosystems of the Sierra Nevada, California](posters/Peek_AGU_2012_poster_optimized.pdf)

 - **Author**, *Affiliation*
 
 > One sentence summary of poster results, objective, or message.

```{r posterAB, out.height='600px', out.width='100%', dpi=300, out.extra='style="background-color: #9ecff7; padding:6px; display: inline-block;"'}

include_graphics("posters/Peek_AGU_2012_poster_optimized.pdf")

```

</div>


## [Using sensitive montane species as indicators of hydroclimatic change in meadow ecosystems of the Sierra Nevada, California](posters/Peek_AGU_2012_poster_optimized.pdf)

 - **Author**, *Affiliation*
 
 > One sentence summary of poster results, objective, or message.

```{r posterABC, out.height='600px', out.width='100%', dpi=300, out.extra='style="background-color: #9ecff7; padding:6px; display: inline-block;"'}

include_graphics("posters/Peek_AGU_2012_poster_optimized.pdf")

```

</div>